\documentclass{revtex4-2}
\bibliographystyle{plain}

% Preamble (add packages and custom commands here)
\usepackage{lipsum} % For generating dummy text
\usepackage{graphicx} % For including figures
\usepackage{float} % For controlling figure placement

% Title section
\begin{document}

\title{K-Means Clustering in Energy Systems}
\author{Felix Weik}
\date{\today}

% Usually an abstract includes the following.
% A brief introduction to the topic that you're investigating. (passt)
% Explanation of why the topic is important in your field/s. (passt)
% Your research question/s / aim/s. (sind drin)
% An indication of your research methods and approach. (auch)
% Your key message.
% A summary of your key findings.
% An explanation of why your findings and key message contribute to 

% Abstract section
\begin{abstract}
Climate change is one of the most pressing issues of our time. 
Its impacts are already visible and will continue to grow in the future.
In the energy sector too, climate change can already be observed, be it the electrical infrastructure collapse due to the Ahrtal flood in 2021 or the Californian wildfires in 2020.
Also, due to increasing climate awareness, people are looking for ways to optimize their energy usage reducing their carbon footprint.

Therefore, this work focuses on a tool to understand energy load patterns and thus improve the design of energy-saving incentives.
This tool is the k-means clustering algorithm.
K-means clustering is one of the most popular and widely used clustering algorithms due to its simplicity and efficiency in handling large datasets.
This work reviews its applications to understand energy load patterns and thus improve the design of energy-saving incentives.
The reviewed papers demonstrate k-means' applications from different perspectives, such as identifying home systems of best practices or reviewing energy efficiency metrics of Chinese industry sectors.

The results show that k-means works well in finding trends and patterns while handling large datasets efficiently.
This generates knowledge out of the data, which can be used as input for higher-level models or decision-making processes.
Also, k-means weaknesses in this area of usage are analyzed, namely the need for a priori knowledge for the value of $k$ or the missing ability to spot single outliers in the data.
The algorithm is efficient in its computational complexity, however, multiple executions are needed to evade the risk of local optima.
This contributes to the understanding of energy load patterns and thus improves the design of energy-saving incentives.

The research shows that k-means can indeed be used to understand energy load patterns and to improve the design of energy-saving incentives.
\end{abstract}

\maketitle

% Introduction section
\include{chapters/2_introduction}

% Methods section
\include{chapters/3_background}

% Evaluation and Results section
\include{chapters/4_findings}

% Discussion section
\include{chapters/5_discussion}

% Outlook section
\include{chapters/6_outlook}

% Conclusion section
\include{chapters/7_conclusion}

% References section (Bibliography)
\bibliography{references} % Include your bibliography file (e.g., references.bib)

\end{document}
