% discuss limitations of the thesis
% potential next steps

% Was möchte ich in diesem Abschnitt vermitteln?
% - Viele eigene Gedanken einbringen
% - Diskutieren, was eventuell besser gemacht werden kann
%   - Können bessere Ergebnisse mit anderen Methoden erzielt werden?
%   - Ist die Arbeit mit anderen Daten sinnvoll?
% - Hat die gegebene Recherche Einschränkungen?

% A case study with larger shares of renewable energy resources in the energy and capacity mix is recommended to investigate the impacts of natural disasters on the renewable-based electricity system [LIU-BDE]

\section{Discussion and Conclusion}
\label{cha:discussionAndConclusion}

% Auf Motivation eingehen
This review aimed to tackle climate change's root causes in the energy sector.
This meant understanding general electricity load patterns and using this knowledge to improve the design of energy-saving incentives.
K-means clustering was introduced as such a tool by applying it to different datasets in the context of two research questions.
The first research questions aimed to generally understand electricity load patterns by identifying patterns and characteristics in a given dataset.
Question two aimed to design energy-saving incentives in the context of private housing and industry.

Both research questions showed, that k-means is a powerful tool for spotting trends and characteristics in data.
It helps to identify the most energy-intensive sectors and companies in big data masses, which helps provide targeted support and reduce information asymmetry \cite{LIU-BDE}.
It identifies different consumer routines and habits in the consumption data which can lay the foundation for applying more advanced methods and theory, thus revealing even more knowledge \cite{MAL-HBP}.
Therefore, k-means is a powerful tool for finding trends, identifying characteristics and revealing hidden knowledge in big data masses.

These applications pointed out the strengths and weaknesses of the k-means algorithm.
% Grundlegende Idee: Auf Limitations und Findings die Stärken und Schwächen von K-Means ausformulieren
% \begin{itemize}
    %     \item Simple and easy to implement and use since a wide range of libraries and tools are available (for example scikit-learn in Python)
    %     \item Effective in spotting general trends
    %     \item Converges every time
    %     \item Linear runtime of $O(n * K * I)$ with $n$ being the number of data points, $k$ being the number of clusters, $i$ being the number of iterations.
% \end{itemize}
The strengths of k-means lie in its simplicity and efficiency in handling big datasets.
Multiple libraries and data analysis tools support the usage of k-means, for example, the r software environment \cite{R-SOF}.
Jessen et al. \cite{JES-IND} showed that k-means is an effective tool for spotting general trends in large datasets.
This also shows that k-means can easily be applied to large datasets like several thousand companies' environmental performance data in Liu et al. \cite{LIU-BDE}.
With its linear runtime of $O(n * K * I)$ ($n$ being the number of data points, $k$ being the number of clusters, $i$ being the number of iterations), k-means executes quickly.
Finally, the algorithm converges every time, so a result is guaranteed \cite{SEL-GCT}.

% \begin{itemize}
    %     \item Failed to spot single outliers in the data
    %     \item Tideous initialization process until actual execution takes place
    %     \item Converges to local instead of global optima => needs to be executed multiple times
    %     \item Despite the algorithm being fast in runtime, running it multiple times and initializing/evaluating the results takes time
    % \end{itemize}
In terms of weaknesses, Jessen et al. \cite{JES-IND} showed that k-means sometimes failed to spot single outliers in the dataset.
Outliers could only be spotted if they followed a general trend or if the dataset had multiple outliers in the same region that could be assigned to a single cluster.
Since the algorithm converges to local optima, it has to be executed multiple times to ensure the correctness of the results.
Furthermore, the initialization process is tedious since the number of clusters has to be provided before the algorithm can be executed.
After finding the optimal number of clusters for the given problem, the initial cluster centers have to be found before being able to execute the algorithm on the given dataset.
This reduces the speed of the fast-executing algorithm in practice.

% Vergleich zu anderen Algorithmen einbauen
Different clustering algorithms have proven to be more effective in improving the mentioned flaws.
K-harmonic means provides superior clustering results in low dimensions compared to k-means \cite{HAM-ALT}.
MAP-DP (Maximum a Posteriori Dirichlet Process) estimates the number of clusters from the data and therefore does not need the number of clusters to be provided beforehand \cite{RAY-ALT}.
Despite being less effective in runtime, MAP-DP is proven to deliver overall better results than k-means \cite{RAY-ALT}.

The reviewed papers showed some limitations and gaps in their research.
% Wie kann man die Limitations der Paper und der Findings auf die zu beantwortenden Research Questions und die Motivation anwenden?
% Also welche Aspekte der Research Question weißen Lücken auf oder wurden unzureichend behandelt?
Some points of the research questions were not fully addressed.

First, the papers were biased toward their choice of energy sources.
Lombok's energy load profiles portrayed by Jessen et al. \cite{JES-IND} stem mostly from fossil fuels.
The living lab in Blackwater, Australia, is powered sustainably by solar and using heat pumps \cite{MAL-HBP}.
Also, each paper focused on a single region with its unique cultural and environmental conditions.
Therefore the findings cannot be generalized or applied to other regions.
This concludes that the design of energy incentives cannot be applied universally by this research alone.
More research and test data using different energy sources and portraying different regions and environmental conditions are needed to fully prove the k-mean's effectiveness in designing energy-saving incentives. 

Additionally, it is not communicated to what extent the COVID-19 pandemic affected the research results.
Malatesta et al. \cite{MAL-HBP} found non-routinized patterns due to people working from home, which most likely is a result of the pandemic and people being forced to stay and work from home, adapting to this new situation.
This can distort the results and make them less applicable to normal conditions.
The pandemic also affects the total energy load profiles, which can lead to false clustering results.
Jessen et al. \cite{JES-IND} detected an increasing energy consumption over the years, especially in 2020 and 2021 but did not check whether these results stem from the pandemic or other factors.
Therefore, the results are not fully reliable and need to be re-evaluated under normal conditions.

Finally, the papers did not prove the correctness of the k-means algorithm's results.
Since the algorithm converges towards local optima, the results are not guaranteed to be the best possible solution.
Therefore, multiple executions are necessary to ensure the correctness of the results.
However, none of the papers performed multiple executions.
This can lead to result manipulation since an incorrect result can prove a wrong hypothesis despite the correct one being present.

The choice of the best clustering algorithm should be guided by the given requirements of the data and the goals of the analysis \cite{COL-ALT}.
K-means clustering is among the most popular clustering algorithms.
This popularity is justified by its simplicity, efficiency in handling big datasets and effectiveness while delivering good results.
One must weigh the balance between efficiently identifying general trends and patterns as suggested by k-means, and more explicit but less effective algorithms.
% "So what" message = How does the written report help the reader in the future?
So, k-means proved as the ideal tool for the given research questions, it is a great starting point in understanding general electricity load patterns and designing energy-saving incentives.

